Hierarchical Dispatching and Overriding

### 2017-09-20 NewVersion/sections/Formalization.tex
more refine

Each method body returns
an expression. As shown in Figure~\ref{fig:syntax}, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.

Expressions can be standard constructs such as variables, method
invocation, or object creation. A novel type of expressions are path-invocations like
``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
implementation for method $m$ should be along the path $I$. Another
interesting expression are super-invocations, which enable a method to access an old
implementation from the specified super type. Hence a super-invocation
can only be used inside an interface definition.
Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
hence they are not supposed to appear in the source program. A value
``$\angl{I}\new{J}$''
is the final result of multiple reduction steps evaluating an
expression. Such value represents an object instance
of $J$ with an annotated static type $I$.

>>>>

The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a method named $m$ with result type $I$, parameters $\overline{x}$ of type $\overline{I_x}$ and the overriding target $J$. The body of the method is the single statement $ \kwreturn \; e;$. We also allow defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is similar as normal method but without a method body. Notebly, We have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.

Expressions can be standard constructs such as variables, method
invocation, or object creation. \name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of expressions: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
implementation for method $m$ should be along the path $I$. 
% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type. Hence a super-invocation can only be used inside an interface definition.
Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
hence they are not supposed to appear in the source program. A value
``$\angl{I}\new{J}$''
is the final result of multiple reduction steps evaluating an
expression. Such value represents an object instance
of $J$ with an annotated static type $I$.
